Search, Compress, Compile: Library Learning in Neurally-Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
Updated colors and compiling

\usepackage{xcolor}
\definecolor{pop1}{HTML}{1f78b4}
\definecolor{pop2}{HTML}{33a02c}
\definecolor{pop3}{HTML}{d95f02}
\definecolor{orange}{HTML}{d95f02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\end{tikzpicture}
  \end{minipage}
\hspace{0.1cm}\begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
      \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (- (length $\ell$) 1))))}\\
      \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
      \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (+ 1 1))))}\\
    \end{tabular}&
    \begin{tabular}{l}
      \code{(map ($\lambda$ (x) (index x $\ell$))}\\
      \phantom{\code{(map)}}\code{(range $\alpha$))}\\
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x $\alpha$) $\beta$ x))) s)}
      \end{tabular}
\\\bottomrule\\
\end{tabular}
\caption{\textbf{Left:} syntax trees of two programs sharing common structure, highlighted in {\color{red} red},
  from which we extract a fragment and add it to the DSL (bottom). \textbf{Right:} actual programs,
  from which we extract fragments that  (top) slice from the beginning of a list or (bottom) perform character substitutions.}\label{fragmentExample}
\end{figure}

>>>>

\usepackage{xcolor}
\definecolor{pop1}{HTML}{1f78b4}
\definecolor{pop2}{HTML}{297F23}
\definecolor{pop3}{HTML}{d95f02}
\definecolor{orange}{HTML}{d95f02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\end{tikzpicture}
  \end{minipage}
\hspace{0.1cm}\begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
      \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (- (length $\ell$) 1))))}\\
      \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
      \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (+ 1 1))))}\\
    \end{tabular}&
    \begin{tabular}{l}
      \code{(map ($\lambda$ (x) (index x $\ell$))}\\
      \phantom{\code{(map)}}\code{(range $\alpha$))}\\
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x $\alpha$) $\beta$ x))) s)}
      \end{tabular}
\\\bottomrule\\
\end{tabular}
\caption{\textbf{Left:} syntax trees of two programs sharing common structure,
highlighted in {\orange{orange}},
  from which we extract a fragment and add it to the DSL (bottom). \textbf{Right:} actual programs,
  from which we extract fragments that  (top) slice from the beginning of a list or (bottom) perform character substitutions.}\label{fragmentExample}
\end{figure}
